The force-free magnetosphere of a Kerr black hole: the role of boundary conditions

### 2018-06-17 paper/ms.tex
abs save

\begin{abstract}
    xx
\end{abstract}

@@

\subsection{Numerical method}
We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition
\be I = 2\Omega A_\phi, \label{eq:rad}\ee
and suitable $\Am(\mu =0, r_+\leq r \leq 2)$
enabling the boundary condition (\ref{eq:bc3}).

1. We choose an initial guess for the field configuration, $\Omega(\Ap)$ and equator boundary condition as follows
\begin{subequations}
\begin{align}
    \Ap &= r^2 \sst,  \label{eq:gss1} \\
    \Omega & = 0.5\WH\left(1-\Ap/\AHE\right), \label{eq:gss2}\\
    \Am(\mu =0, r_+\leq r \leq 2) & = -1\times (r/r_+)^3. \label{eq:gss3}
\end{align}
\end{subequations}

2. We evolve the GS equation and find $II'$ enabling smooth field lines across the LS
\cite[see][for details]{Contopoulos2013, Nathanail2014, Pan2016a}.

3. Usually the current $I$ found in Step 2 neither satisfies the radiation condition (\ref{eq:rad})
nor enables the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
$\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
\be
 A_{\phi,\mu\rm new}  = A_{\phi,\mu \rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
\ee
enabling the radiation condition (\ref{eq:rad}) for
$A_\phi\in [A_\phi^{\rm HE}, A_\phi^{\rm EE}]$, where $\zeta_1$ is an
empirical step size.

4. The final step is to adjust  $\Omega(\Ap < \AHE)$ enabling  the radiation condition (\ref{eq:rad})
 for $A_\phi < A_\phi^{\rm HE}$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
 enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in [\AHE, \AEE]$.
 The first part is straightforward, i.e.,
 \be
\Omega_{\rm new}(\Ap < \AHE) = \frac{I}{2\Ap},
 \ee
 and the second part can be realized by
 \be
\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Big|_{\mu=0, r_+\leq r \leq 2}
 \ee
 where $\zeta_2$ is again an empirical step size, and we have multiplied factor $\Delta$
 to avoid numerical difficulty in the vicinity of the event horizon. To avoid unphysical discontinuity in the angular
 velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ via a fifth-order polynomial.

 5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat step 2 to step 4,
 until the numerical prescription (\ref{eq:nbc}) is satisfied.

>>>>

\begin{abstract}
    The role of boundary conditions in the structure of
    a force-free black hole magnetosphere was rarely discussed, since previous studies have been focused on the
    the field lines entering the horizon which is causally disconnected and on which the boundary
    condition imposed usually makes no difference to the magnetosphere structure. However,
    recent high-resolution general relativistic (GR) force-free simulation shows that there are both
    field lines entering the horizon and field lines ending up on the equatorial current sheet
    within the ergosphere for asymptotic uniform field. For the latter, the equatorial boundary
    condition is well approximated being marginally force-free, i.e., $B^2-E^2=0$, where $B$ and
    $E$ are the magnetic and electric field strength, respectively. In this paper, we revisit this
    problem by solving the GR Grad-Shafranov equation which governs the structure of
    the force-free magnetosphere in steady state and self-consistently imposing the marginally force-free equatorial
    condition. We also discuss the applicability of this boundary condition and the numerical algorithm proposed
    in this paper for general magnetic field configurations.
\end{abstract}

@@

\subsection{Numerical method}
We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition
\be I = 2\Omega A_\phi, \label{eq:rad}\ee
enabling field lines smoothly crossing the LS,
and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
guaranteeing the boundary condition (\ref{eq:bc3}).

In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
and implement a uniform $512\times 64$ grid. The detailed algorithm is listed as follows.

1. We choose an initial guess for the field configuration, $\Omega(\Ap)$, $I(\Ap)$
and equator boundary condition as follows
\begin{subequations}
\begin{align}
    \Ap &= r^2 \sst,  \label{eq:gss1} \\
    \Omega & = 0.5\WH\left(1-\Ap/\AHE\right),  \label{eq:gss2}\\
    I & = \WH \Ap\left(1-\Ap/\AHE\right) , \\
    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3. \label{eq:gss3}
\end{align}
\end{subequations}

2. We evolve the GS equation (\ref{eq:GSg}) and adjust $II'(\Ap)$ enabling smooth field lines across the LS
\cite[see e.g.][for details]{Contopoulos2013, Nathanail2014, Pan2016a, Mahlmann2018}.

3. Usually the current $I$ found in Step 2 neither satisfies the radiation condition (\ref{eq:rad})
nor guarantees the boundary condition (\ref{eq:bc3}). We find it is possible to adjust
$\Am(\mu = 0, r_+ \leq r\leq 2)$ as follows
\be
 A_{\phi,\mu}|_{\rm new}  = A_{\phi,\mu}|_{\rm old} + \zeta_1\times[2\Omega\Ap(2\Omega\Ap)' -II'],
\ee
enabling the radiation condition (\ref{eq:rad}) for
$A_\phi\in [A_\phi^{\rm HE}, A_\phi^{\rm EE}]$, where $\zeta_1$ is an
empirical step size.

4. The remaining task is to adjust  $\Omega(0< \Ap < \AHE)$ enabling  the radiation condition (\ref{eq:rad})
 for $A_\phi \in (0, A_\phi^{\rm HE})$ and  to adjust $\Omega(\AHE \leq \Ap \leq \AEE)$
 enabling the boundary condition (\ref{eq:bc3}) for $\Ap \in [\AHE, \AEE]$.
 The first part is straightforward, i.e.,
 \be
\Omega_{\rm new} = \frac{I}{2\Ap}\Bigg|_{0 < \Ap < \AHE},
 \ee
 and the second part can be realized by
 \be
\Omega_{\rm new}  = \Omega_{\rm old} - \zeta_2\times\frac{\Delta (B^2-E^2)}{2\Ap}\Bigg|_{\mu=0, r_+\leq r \leq 2},
 \ee
 where $\zeta_2$ is again an empirical step size, and we have multiplied factor $\Delta$
 in the correction term to avoid numerical difficulty in the vicinity of the event horizon.
 To eliminate unphysical discontinuity in the angular
 velocity at $\AHE$, we fit $\Omega_{\rm new}(\Ap)$ on the whole range
 $[0, \AEE]$ via a fifth-order polynomial.

 5. For the new angular velocity $\Omega_{\rm new}(\Ap)$ obtained in Step 4, we repeat step 2 to step 4,
 until the numerical prescription (\ref{eq:nbc}) for the boundary condition (\ref{eq:bc3}) is satisfied.
